Flat-histogram method comparison on the 2D Ising model

### 2020-05-08 ising/ising-body.tex
more verbiage on the production run results

\subsection{128 $\times$ 128 Ising system}
For the larger 2D Ising system, the update factors initially
start at the same $\gamma_{t=0} = 1$; however, all of the methods take longer
to proceed as $1/t$ (with SAD taking $10^{13}$ moves). Fig.~\ref{fig:N128-gamma} shows the update factor $\gamma_t$ for each of the 
flat-histogram methods. 
We implement two WL simulations followed by a production run each beginning
after $\gamma^{\text{WL}}_t$ has reached $10^{-4}$ and $10^{-6}$ respectively.
Fig.~\ref{fig:N128-cv-error} shows the maximum error in the heat capacity as a 
function of time for this system. The solid/dashed lines represent the maximum
value of the error in the specific heat capacity $c_V$ averaged
over eight simulations using different random number seeds. The range of maximum
errors for each simulation is shown as a shaded region. By
the time $10^{13}$ moves have been made all but the WL simulation have begun to
converge as $1/\sqrt{t}$. We then see the WL error saturate around $10^{12}$
moves. The two WL simulations followed by a production run highlight that
choosing too large a $\gamma^{\text{WL}}_t$ will result in poor convergence
properties.

>>>>

\subsection{128 $\times$ 128 Ising system}
For the larger 2D Ising system, the update factors initially
start at the same $\gamma_{t=0} = 1$; however, all of the methods take longer
to proceed as $1/t$ (with SAD taking $10^{13}$ moves). Fig.~\ref{fig:N128-gamma} shows the update factor $\gamma_t$ for each of the 
flat-histogram methods. 
We implement two WL simulations followed by a production run each beginning
after $\gamma^{\text{WL}}_t$ has reached $10^{-4}$ and $10^{-6}$ respectively.
Fig.~\ref{fig:N128-cv-error} shows the maximum error in the heat capacity as a 
function of time for this system. The solid/dashed lines represent the maximum
value of the error in the specific heat capacity $c_V$ averaged
over eight simulations using different random number seeds. The range of maximum
errors for each simulation is shown as a shaded region. By
the time $10^{13}$ moves have been made all but the WL simulation have begun to
converge as $1/\sqrt{t}$. We then see the WL error saturate around $10^{12}$
moves.  The WL simulation followed by a production run when
$\gamma^{\text{WL}}_t$ reached $10^{-4}$ sometimes dramatically failed to
converge, and with a \davidsays{few} random seeds converged very
nicely.  This highlights a risk taken when setting $\gamma^{\min}$.
If the weights are insufficiently converged, the production run will
fail to explore all energies. \davidsays{Can you identify whether it got
stuck at high or low energy?}  With the smaller value of
$\gamma^{\min}=10^{-6}$ consistently and efficiently converged.

%% The two WL simulations followed by a production run highlight that
%% choosing too large a $\gamma^{\text{WL}}_t$ will result in poor convergence
%% properties.
